The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-07-20 head.tex

% highlight the novel aspects of the work, indicating the relevance of the paper to the conference topics

% What I do yet :
% Construct the ecosystem frame work
% study the manufacturing cooperation method with each other.
% Design the trading the method
% Simulation (agent-based model) and analysis.

% Supplier evaluation and selection constitutes a central issue in supply chain management (SCM). How- ever, the data on which to base the corresponding choices in real life problems are often imprecise or vague, which has led to the introduction of fuzzy approaches. Predictive intelligent-based techniques, such as Artificial Neural Network (ANN) and Adaptive Neuro Fuzzy Inference System (ANFIS), have been recently applied in different research fields to model fuzzy multi-criteria decision processes where the understanding and learning of the relationships between the input and output data are the key to select suitable solutions. In this paper, a hybrid ANFIS-ANN model is proposed to assist managers in their sup- plier evaluation process. After aggregating the data set through the Analytical Hierarchy Process (AHP), the most influential criteria on the suppliers¡¯ performance are determined by ANFIS. Then, Multi-Layer Perceptron (MLP) is used to predict and rank the suppliers¡¯ performance based on the most effective criteria. A case study is presented to illustrate the main steps of the model and show its accuracy in prediction. A battery of parametric tests and sensitivity analyses has been implemented to evaluate the overall performance of several models based on different effective criteria combinations.

% Basically, (present what have done)

% we do not use any utility function for the modeling; however, a unique method is proposed for eliciting the information from decision makers. The proposed model is applicable for a wide variety of multi-attribute decision making problems and can be used for  future ranking or selection without managers' judgment effort. Simulation of the managers' decisions is demonstrated in detail and the design and implementation of the model are illustrated by case study.

% The research was conducted in three steps: (1) existing concepts and models for industrial sustainability were reviewed and environmental practices in manufacturing were collected and analysed; (2) gaps in knowledge and practice were identified; (3) the outcome is a manufacturing ecosystem model based on industrial ecology (IE)

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Cloud manufacturing ecosystem \sep
Resource servitization and optimization\sep
Service pattern recognition\sep
Manufacturing evolution\sep
Agent-based simulation

%Cloud Manufacturing  Ecosystem \sep scheduling \sep evolving \sep optimization
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}

>>>>

@@

\begin{keyword}
Cloud manufacturing ecosystem \sep
Resource servitization and optimization\sep
Service pattern recognition\sep
Manufacturing evolution\sep
Agent-based simulation

\end{keyword}
